\documentclass{scrartcl}

\usepackage{url}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{varwidth}
\usepackage[dvipsnames]{xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{listings}
\lstset{
	basicstyle=\footnotesize\ttfamily,
	tabsize=4,
	showstringspaces=false,
	breaklines=true,
	prebreak={\space\hbox{\textcolor{Gray}{$\hookleftarrow$}}},
	language=C++
}
\usepackage{enumitem}

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\tikzstyle{flowchartnode} = [rectangle, minimum height=0.8cm, text centered, text width=3cm, draw=black, font=\small]
\tikzstyle{startstop} = [flowchartnode, rounded corners=0.4cm]
\tikzstyle{process} = [flowchartnode]
\tikzstyle{io} = [flowchartnode, trapezium, trapezium left angle=70, trapezium right angle=110, text width=2cm]
\tikzstyle{decision} = [flowchartnode, diamond, aspect=2, text width=2cm]
\tikzstyle{arrow} = [thick,->,>=stealth]

\makeatletter
\@addtoreset{section}{part}
\makeatother  

\title{Worksheet 4}
\subtitle{COMP110: Principles of Computing}
\author{Ed Powley}
\date{January 2016}

\renewcommand\thepart{\Alph{part}}

\begin{document}

\maketitle

\section*{Introduction}

In this assignment, you will create two small C++ programs:
\begin{enumerate}[label=\Alph*.]
	\item A console application implementing the ``terminal hacking'' word-guessing minigame from the Fallout games;
%	\item A console application implementing the 2-player board game Connect~4;
	\item A graphical application which generates and displays the Mandelbrot fractal.
\end{enumerate}

This worksheet tests your ability to translate various program notations (pseudocode, flowcharts,
mathematics, narrative descriptions) into C++ code.

\section*{Submission instructions}

The GitHub repository at the following URL contains skeleton projects for the two parts of this worksheet.
\begin{center}
\url{https://github.com/Falmouth-Games-Academy/comp110-worksheet-4}
\end{center}
Fork this repository into your own GitHub account. To submit, create a GitHub pull request.

For the most part, this worksheet requires you to edit C++ code in the skeleton projects provided.
\textbf{Please do not rename or delete the projects or files provided, and please do not create new projects.}
This will ensure that GitHub's ``diff'' view highlights only the parts of the code that you have edited.
Creating new source and/or header files is permitted, if doing so improves the structure of your programs.

\section*{Marking}

\subsection*{Timely submission: $40\%$}

The deadline for this worksheet is \textbf{6pm, Wednesday 10th February 2016}.
To obtain the marks for timely submission, you must submit (as a GitHub pull request) your progress towards \textbf{both} parts of the worksheet by this time.
As with other worksheets, you may resubmit after these deadlines in order to collect extra correctness or quality marks.
This $40\%$ is awarded as long as you submit \emph{something} for each part by the deadline,
even if your submission has bugs or other issues.

\subsection*{Correctness: $30\%$}

To obtain the marks for correctness, you must submit working solutions for the following:
\begin{itemize}
\item Part~A, Sections~\ref{core-a-first}--\ref{core-a-last};
\item Part~B, Sections~\ref{core-c-first}--\ref{core-c-last}.
\end{itemize}
Note that this is a threshold: the full $30\%$ is awarded for work which is \emph{complete}
and contains \emph{no clear errors}. In particular you will not be penalised for trivial errors which do not
affect the overall functioning of your programs, nor will you receive extra credit for highly polished solutions.

\subsection*{Quality: $30\%$}

The extra quality criteria for this worksheet are as follows. All are weighted equally, so each is worth $6\%$ of the overall mark for this worksheet.
\begin{enumerate}
\item\textbf{Presentation.} Your solutions are appropriately presented in GitHub, with descriptive commit messages
	and appropriate documentation in \texttt{readme.md} files.
	You have edited the provided skeleton projects, and refrained from renaming the provided files or creating new projects.
    You have checked code into GitHub regularly whilst working on the worksheet.
\item\textbf{Code quality.} Your code is well formatted.
    Variable and function names are clear and descriptive.
    Comments are used where appropriate, and are well written.
    Your formatting, naming and commenting follow consistent conventions.
\item\textbf{Part A stretch goal.} You have submitted a working solution for Part~A, Section~\ref{stretch-a} (an improved word selection algorithm for the terminal hacking game).
%\item\textbf{Part B stretch goal.} You have submitted a working solution for Part~B, Section~\ref{stretch-b} (a rule variant for Connect~Four).
\item\textbf{Part B stretch goal.} You have submitted a working solution for Part~B, Section~\ref{stretch-c} (a generator for a fractal other than the Mandelbrot set).
\item\textbf{Sophistication.} Your solution for \textbf{either} of the stretch goals is particularly sophisticated,
	demonstrating mastery of C++ programming concepts appropriate to the task at hand.
    (N.B.: the emphasis here is on \emph{appropriate}; you will not receive extra credit for shoehorning advanced constructs into your code where a simpler solution would have sufficed.)
\end{enumerate}

\clearpage
\input{parta}

%\clearpage
%\input{partb}

\clearpage
\input{partc}

\end{document}
