\documentclass{../../fal_assignment}
\graphicspath{ {../../} }

\usepackage{enumitem}
\setlist{nosep} % Make enumerate / itemize lists more closely spaced
\usepackage[T1]{fontenc} % http://tex.stackexchange.com/a/17858
\usepackage{url}
\usepackage{todonotes}

\title{Brief from the Publisher}
\author{Dr Michael Scott}
\module{COMP150}

\begin{document}

\section*{Brief from the Publisher - Ninja Nyan Play Lab}

At \textit{Ninja Nyan Play Lab}, we fund and publish accessible historical-fantasy games for mobile devices and social networking platforms. 

We typically target mature audiences interested in simple, and retro-themed games, but will consider other demographics where a compelling argument is made and the proposal's thematic is compatiable with our existing catalogue of game titles.

In this round of funding, we are particular interested in a top-down 2D game that leverages techniques in procedural content generation to present a sprawling virtual world.

As a commercial publisher and are able to provide seed funding of up to \textsterling~250,000 to develop well-scoped and innovate games beyond the prototyping stage; however, we expect a return on our investment above stock-market rates ($\approx 110\%$ growth) within 18 months. You must clearly present the unique selling points of and a clear value proposition to be considered for funding. 

\subsection*{Constraint \#1 - Genre}
2D top-down `dungeon' crawler.

\subsection*{Constraint \#2 - Audience}
Social network users, ages 27 to 37.

\subsection*{Constraint \#3 - Theme}
Historical fantasy.

\subsection*{Constraint \#4 - Platform}
Mobile and PC. 

Please note, we don't need to see a mobile prototype version, we have an in-house porting team. Please develop your prototype demonstration in Python for PC. Use a window dimension of 750x1334 (landscape) or 1334x750 (portrait) in line with Apple's standard for iPhone.

\subsection*{Constraint \#5 - Accessible}
The game should be accessible to those with impaired colour vision as a minimum. The control system should be simple enough for casual use in environmental contexts that can impair motor skills, such as cars, planes, and ships.

\subsection*{Constraint \#6 - Scoping the Feature Set}

A minimalist but compelling set of features is desired. For the purposes of this prototype demo, the core mechanic(s) (typically, a single character exploring a dungeon and interacting with non-player entities), all features (as critical for the design), and instructions (on how to play) should be captured within a 15-minute play session.

\end{document}