\chapter{COMP320 Assignment: Proposal}

\section*{Introduction}

You are required to deliver a major \textbf{research project} as part of your degree; either in the form of \textbf{empirical research} relating to computing for games, or \textbf{practice-based research} related to game development. Individually, you explore a field that interests you, and for which there is a clearly identified need. This module forms the first part of this project and provides the opportunity to conduct a literature review, as well as to collect and analyse data using appropriate methods and statistics.

These assignments are formed of several parts:

\begin{enumerate}[label=(\Alph*)]
	\item \textbf{Identify} a project supervisor \textbf{and agree} a topic for your research, by:
		\begin{enumerate}[label=(\roman*)]
			\item \textbf{reviewing} the academic literature \textbf{in addition to} the state-of-the-art
			\item \textbf{and deriving} a key question or problem from the review to motivate your work
		\end{enumerate}
	\item \textbf{Produce} a prototype computing artefact that will:
		\begin{enumerate}[label=(\roman*)]
			\item \textbf{facilitate} the collection of empirical data for your project
			\item \textbf{demonstrate} the technical feasibility of your proposed artefact
			\item \textbf{provide} a basis for further development and
				experimentation in the second study block
		\end{enumerate}
		\textbf{Note that you \textit{must} complete and submit Part C
		\textit{before} carrying out any experimental work.}
	\item \textbf{Complete} an Application for Research Ethics Approval form,
		which will:
		\begin{enumerate}[label=(\roman*)]
			\item \textbf{briefly propose} the research to be undertaken in your project
			\item \textbf{outline} any potential ethical issues around your proposed work,
				particularly with respect to research involving human subjects
		\end{enumerate}
	\item \textbf{Incorporate} computational statistics into your prototype computing artefact, indicating how you will:
		\begin{enumerate}[label=(\roman*)]
			\item \textbf{collect, analyse, and present} data relevant to your research
		\end{enumerate}
	\item \textbf{Deliver} a 10-minute practice presentation that will:
		\begin{enumerate}[label=(\roman*)]
			\item \textbf{explain} the context of your project
			\item \textbf{identify} and \textbf{discuss} the scientific literature
				relevant to your project
			\item \textbf{propose} one or more research questions for your project
			\item \textbf{articulate} the ethical considerations you have made
			\item \textbf{illustrate} your approach to collecting, analysing, and presenting data
		\end{enumerate}
	\item \label{part:review-draft} \textbf{Write} a draft research review and proposal
		that will:
		\begin{enumerate}[label=(\roman*)]
			\item \textbf{identify} and \textbf{analyse} the scientific literature
				relevant to your project
			\item \textbf{propose} one or more research questions for your project
			\item \textbf{justify} your choice of research question(s)
				and how they will contribute to the state of knowledge
			\item \textbf{justify} the methodology to be used
				in addressing the research question(s)
			\item \textbf{outline} the key legal, social, ethics, and professional considerations	
			\item \textbf{present} your data analysis approach \textbf{and} any preliminary results
		\end{enumerate}
	\item \textbf{Write} a final research review and proposal that will:
		\begin{enumerate}[label=(\roman*)]
			\item \textbf{address} any issues raised in Part~\ref{part:review-draft}
		\end{enumerate}
	\item \textbf{Deliver} a 10-minute presentation that will:
		\begin{enumerate}[label=(\roman*)]
			\item \textbf{summarise} the context and research question(s)
				of your project
			\item \textbf{outline} and \textbf{justify} the methodology to be used in
				addressing the research question(s)
			\item \textbf{assess} legal, social, ethical, and professional issues
			\item \textbf{present} any preliminary results you have obtained so far, \textbf{emphasising} your
				approach to data collection, analysis, and presentation
		\end{enumerate}
\end{enumerate}

\subsection*{Assignment Setup}

These assignments form a \textbf{research} task, consisting of \textbf{literature review}, \textbf{academic writing},
\textbf{software development} and \textbf{scientific experimentation}. For the \textbf{research proposal} with \textbf{prototype computing artefact}, there are no set git repositories or templates for you to use. Though, you may choose to use one or more of the templates available on our GitHub Enterprise Server: \indent \url{https://github.falmouth.ac.uk}

You are strongly encouraged to use a repository for your prototype computing artefact in order to demonstrate your refactoring process. Ensure that you set up the \texttt{.gitignore} file for your chosen development environment, and maintain the \texttt{readme.md} file with design documentation appropriate to your project. Select a suitable license for your work.

For the written component, you may use IEEE Transactions style or ACM style, to write your research proposal. There are templates available on LearningSpace.

\subsection*{Part A}

Part A consists of a \textbf{single formative submission} early in academic year, by a date agreed with your supervisor.
This work is \textbf{individual} and will be assessed on a \textbf{threshold} basis.

To complete Part A, email your chosen supervisor and agree a topic for your proposal within the area of that
supervisor's expertise. Then, email confirmation of that agreement to the module leader.

You will receive immediate and continuous \textbf{informal feedback} through timetabled weekly meetings with your supervisor.

\subsection*{Part B}

Part B consists of a \textbf{multiple formative submissions},
set at the discretion of your project supervisor based on agreed milestones and the nature of your proposed project.
This work is \textbf{individual} and will be assessed on a \textbf{threshold} basis.

To complete Part B, design and implement a computing artefact appropriate to your chosen project.
Create a task board setting out the key requirements for the system,
and identifying which requirements will be tackled this study block
and which are stretch goals to be left until later.
Check the source code into a version control repository regularly.
Ensure your \texttt{readme.md} file contains any information required to build and run the artefact as well as
relevant design documentation (including relevant UML diagrams).

You will not directly submit this work. Instead, your supervisor will track your work on the BitBucket server.

You will receive immediate and continuous \textbf{informal feedback} through meetings with your supervisor.

\todo[inline]{\textbf{Important:} Carrying out \textbf{any} data collection or experimental work
without first securing ethical approval is a breach of Falmouth University's Research Ethics Policy.
This will be treated as a case of academic misconduct, and penalised accordingly.}

\subsection*{Part C}

Part C consists of a \textbf{single formative submission}.
This work is \textbf{individual} and will be assessed on a \textbf{threshold} basis.

To complete Part C, download the Research Ethics Approval Application Form
from the LearningSpace. Complete the form in consultation with your project supervisor.
Note that you will need to write a (brief) research proposal for this form. Print and sign the form, 
and hand it to your supervisor for approval.

You will receive immediate \textbf{informal feedback} from your supervisor and a \textbf{decision} 
after the ethics committee have convened, according to the academic calendar.

\subsection*{Part D}

Part D consists of a \textbf{multiple formative submissions},
set at the discretion of your project supervisor based on agreed milestones and the nature of your proposed project.
This work is \textbf{individual} and will be assessed on a \textbf{threshold} basis.

To complete Part D, incorporate computational statistics into the repository of your prototype computing artefact.
It is anticipated that you will write \texttt{R} code or \texttt{NumPy} code (or similar) to support your use of data in your project.
Ensure your \texttt{readme.md} file contains any information required to build and execute your statistical tests.

If you have not yet conducted a pilot study, it is advisable to generate sample data through simulation so that you can 
prepare your data analysis and presentation techniques.

You will receive immediate and continuous \textbf{informal feedback} through meetings with your supervisor.

\subsection*{Part E}

Part E consists of a \textbf{single formative submission}.
This work is \textbf{individual} and will be assessed on a \textbf{threshold} basis.
To pass, answer the following questions:

\begin{enumerate}[label=(\roman*)]
	\item What is the context of your project? How does it fit into the
		research field of computing for games?
	\item What are the key results from the literature upon which your project will be built?
	\item What is the current state of knowledge in the field?
		What are the open questions and challenges?
	\item What is (are) the key research question(s) that you will seek to
		answer in your project?
	\item What are the key legal, social, ethical, and/or professional issues 
		associated with your project?
\end{enumerate}

To complete Part E, prepare a short presentation 
and deliver it to your supervisor in your last scheduled supervision meeting.
Prepare your slides using your choice of presentation software
(e.g.\ Beamer, reveal.js, PowerPoint).

You will receive immediate \textbf{informal feedback} from your tutor.

\subsection*{Part F}

Part F consists of a \textbf{single formative submission},
however your project supervisor may also set additional \textbf{formative submissions} at their discretion.
This work is \textbf{individual} and will be assessed on a \textbf{threshold} basis.

To complete Part F, use the provided LaTeX template to write a literature review and proposal. Then, attend the 
relevant session in week~12.

Do \textbf{not} modify the formatting of the provided template. You are advised to bear in mind the page limit 
and attempt to adhere to it at this stage, however you will \textbf{not} be penalised for failing to do so. 
Please also ensure that you include a clear link to your git repo somewhere in the document.

You will receive immediate \textbf{informal feedback} from your peers.

\subsection*{Part G}

Part G consists of a \textbf{single summative submission},
however your project supervisor may also set additional \textbf{formative submissions} at their discretion.
This work is \textbf{individual} and will be assessed on a \textbf{holistic} basis,
according to the descriptors set out at the end of this document.

To complete Part G, revise your document from Part E
to address any issues highlighted during the peer review. Also, incorporate references to the data analysis
approaches that you intend to deploy (as per Part F).
Your document must not exceed \textbf{six pages} of text,
excluding figures, tables, references and appendices.
This is subject to the usual policy on word and page limits available on LearningSpace.

Please ensure that you include a clear link to your git repo somewhere in the document.

Upload your final \texttt{.pdf} file to the LearningSpace.
Note that LearningSpace will only accept a single \texttt{.pdf} file.

You will receive \textbf{informal feedback} through a meetings with your supervisor.
You will also receive \textbf{formal feedback} three weeks after the deadline.

\subsection*{Part H}

Part H consists of a \textbf{single formative submission}.
This work is \textbf{individual} and will be assessed on a \textbf{threshold} basis.
To pass, answer the following questions:

\begin{enumerate}[label=(\roman*)]
	\item What is (are) the key research question(s) that you will seek to
		answer in your project?
	\item How will answering these questions contribute to the state of knowledge
		in the field of your project?
	\item What methodology will you use to seek answers to these questions?
		Justify your methodology.
	\item What preliminary results have you obtained?
\end{enumerate}

To complete Part H, prepare a short presentation 
and deliver it in the scheduled session in week~13.
Prepare your slides using your choice of presentation software
(e.g.\ Beamer, reveal.js, PowerPoint).

You will receive immediate \textbf{informal feedback} from a panel of academics.
You will also receive \textbf{formal feedback} three weeks after the deadline.

\section*{FAQ}

\begin{itemize}
	\item 	\textbf{What is the deadline for this assignment?} \\ 
    		Falmouth University policy states that deadlines must only be specified on the MyFalmouth system.
    		
	\item 	\textbf{What should I do to seek help?} \\ 
    		You can email your tutor for informal clarifications. For informal feedback, make a pull request on GitHub. 
    		
    	\item 	\textbf{Is this a mistake?} \\ 	
    		If you have discovered an issue with the brief itself, the source files are available at: \\
    		\url{https://github.com/Falmouth-Games-Academy/bsc-assignment-briefs}.\\
    		 Please make a pull request and comment accordingly.
\end{itemize}

Note that the assignments which constitute your dissertation project are \textbf{not} marked in a criterion-based fashion.
Instead, your project supervisor will assign an overall grade by considering the following descriptors in relation to your project.

\newpage

\rubrictitle{Proposal with Computing Prototype}

\rubrichead{All submissions and assessment criteria for this assignment are individual.

To \textbf{pass} this assignment (achieve 40\% or more), you \textbf{must} successfully defend a response to a research opportunity, using appropriate methods, evidence, and conventions. You \textbf{must} also adequetely evaluate legal, social, ethical, and professional issues in projects in correspondence with the relevant law, codes of conduct, and theory and you \textbf{must} also synthesise knowledge of computing to address complex technical challenges. In doing so, you will demontrate an adequate ability to generate ideas, problem solving, concepts, technical competency and proposals in response to set briefs and/or self-initiated activity alongside an adequate, ethically informed, real-world experience of industry/business environments and markets. You will also demonstrate adequate research and information skills.

Please note that you must pass every assessment criterion to pass the assignment overall.
}

\begin{markingrubric}
    \firstcriterion{Ethics Approval}{---}
		\grade\fail An ethics approval form has not been submitted.
			\par \textbf{This is an automatic fail, regardless of other criteria.}
		\grade Ethics approval has been sought and obtained.
	%
    \criterion{Basic Competency Threshold}{---}
		\grade\fail Parts~B and~C are not completed or are unsatisfactory.
			\par Referencing of sources is unsatisfactory.
		\grade A satisfactory presentation is delivered for Part~B.
			\par The student participates in the peer review activity for Part~C, with enough work present for a meaningful review.
			\par Sources are referenced, with no obvious errors or omissions.
	%
    \criterion{Breadth of literature review}{---}
        \grade \fail 	The literature review is missing or unsatisfactory.
        	\par 		Many key sources are omitted.
        \grade 		The literature review falls far short of comprehensive.
        	\par 		There are many obvious omissions.
        \grade		The literature review falls short of comprehensive.
        	\par 		There are some obvious omissions.
        \grade 		The literature review is somewhat comprehensive.
        	\par 		There are few obvious omissions.
        \grade		The literature review is very comprehensive.
        	\par 		There are very few obvious omissions.
        \grade		The literature review is extremely comprehensive.
        	\par 		There are no obvious omissions.
	%
    \criterion{Depth of insight}{---}
        \grade\fail 	Little insight is demonstrated.
        \par		Papers are summarised in the student's own words.
        \grade		Some insight is demonstrated.
        \par		Attempts are made at discussion beyond summary.
        \grade		Much insight is demonstrated.
        \par		Discussion is inferential in nature.
        \grade		Considerable insight is demonstrated.
        \par		Discussion is analytical in nature.
        \grade		Significant insight is demonstrated.
        \par		Discussion is analytical and evaluative in nature.
        \grade		Extensive insight is demonstrated.
        \par		Discussion is analytical and evaluative in nature.
	%
    \criterion{Specificity, verifiability \& accuracy of claims}{---}
        \grade\fail 	Few claims have a clear source of evidence.
        \par 		Significant errors and/or misinterpretations.
        \grade 		Some claims have a clear source of evidence.
        \par 		Many errors and/or misinterpretations.
        \grade 		Many claims have a clear source of evidence.
        \par 		Some errors and/or misinterpretations.
        \grade 		Most claims have a clear source of evidence.
        \par 		Few errors and/or misinterpretations.
        \grade 		All claims have a clear source of evidence.
        \par 		Almost no errors and/or misinterpretations.
        \grade 		All claims have a clear source of evidence.
        \par 		No errors and/or misinterpretations.
    %
    \criterion{Quality of research question(s)}{---}
        \grade\fail 	Research questions are absent or not satisfactory.
        \grade 		Research questions show basic understanding of the field.
        \par		Research questions are unambitious or unoriginal.
        \grade 		Research questions show strong understanding of the field.
        \par		Research questions are original.
        \grade 		Research questions show some insight into the field.
        \par		Research questions are original and ambitious.
        \grade 		Research questions show much insight into the field.
        \par		Research questions are original, ambitious and timely.
        \grade 		Research questions show significant insight into the field.
        \par		Research questions are at the cutting edge of the field.
    %
\end{markingrubric}
    
\begin{markingrubric}
        \firstcriterion{Description of Computing Artefact}{---}
        \grade\fail 	There is little to no indication of what the computing artefact is and/or where the prototype can be found.
        \grade 		There is an adequate description of the computing artefact. 
        \par		There is a hyperlink in the document to the repository containing the source code.
        \grade 		There is a competent description of the computing artefact, supplemented with relevant diagrams, source code excerpts and/or screenshots.
        \par		There is a clear hyperlink to the repository containing the source code.
        \grade 		There is a very good description of the computing artefact, supplemented with appropriate diagrams, source code excerpts and/or screenshots.
        \par		There is a very clear hyperlink to the repository containing the source code.
        \grade 		There is an excellent description of the computing artefact, supplemented with appropriate diagrams, source code excerpts and/or screenshots. 
        \par		Design considerations and constraints are articulated well. 
        \par 		There is a very clear hyperlink to the repository containing the source code.
        \grade 		There is an excellent description of the computing artefact, supplemented with appropriate diagrams, source code excerpts and/or screenshots.
        \par		Design considerations and constraints are illustrated elegantly. 
        \par 		There is a very clear hyperlink to the repository containing the source code.
    %
    \criterion{Methodology}{---}
        \grade\fail 	Methodology is not specified, not justified, or either of these is unsatisfactory.
        \grade 		The proposed methodology is somewhat plausible.
        \par		The justification is not very convincing.
        \grade 		The proposed methodology is plausible.
        \par		The justification is somewhat convincing.
        \grade 		The proposed methodology is sound.
        \par		The justification is convincing.
        \grade 		The proposed methodology is very sound.
        \par		The justification is very convincing.
        \grade 		The proposed methodology is extremely sound.
        \par		The justification is extremely convincing.
%
     \criterion{Ethical Considerations}{---}
        \grade\fail 	Inadequete assessment of legal, social, ethical, and professional issues.
         \par		The proposed project is not ethically sound.
        \grade 		There is a somewhat accurate assessment of legal, social, ethical, and professional issues.
        \par		The proposed project is ethically sound, but there may be several concerns to address through the approval process.
        \grade 		There is an accurate assessment of legal, social, ethical, and professional issues; accompanied by a somewhat sensible analysis of key concerns.
        \par		The proposed project is ethically sound, but there may be a few concerns to address through the approval process.
        \grade 		There is an accurate assessment of legal, social, ethical, and professional issues; accompanied by a sensible analysis of key concerns.
        \par		The proposed project is ethically sound, and there a little to no concerns.
        \grade 		There is an accurate and comprehensve assessment of legal, social, ethical, and professional issues; accompanied by a sensible discussion of prominent concerns.
        \par		The proposed project is ethically sound, and there a little to no concerns.
        \grade 		There is an accurate and comprehensive assessment of legal, social, ethical, and professional issues; accompanied by a deeply intellectual discussion of prominent concerns.
        \par		The proposed project is ethically sound, and there a little to no concerns.
%
\end{markingrubric}

\begin{markingrubric}
    \firstcriterion{Data Management Plan}{---}
        \grade\fail 	There is little to no description of how to collect, analyse, and present data.
        \grade 		There is an adequete description of how to collect, analyse, and present data to support the research process.
         \par		The proposed use of computational statistics is described with some clarity.        
        \grade 		There is a competent explanation of how to collect, analyse, and present data to support the research process.
         \par		The proposed use of computational statistics is sensible and is described clearly.         
        \par		Excerpts of the data analysis code are present and described accurately.                 
        \grade 		There is a very good analysis of how to collect, analyse, and present data to support the research process.
         \par		The proposed use of computational statistics is well devised and has been defined with precision.                  
        \par		Excerpts of the data analysis code are present and are well explained.   
        \grade 		There is an excellent evaluation of how to collect, analyse, and present data to support the research process.
         \par		The proposed use of computational statistics is very well devised and has been defined in a way that supports replication.      
        \par		A walkthrough of the data analysis code is present and is justified.   
        \grade 		There is an outstanding description of how to collect, analyse, and present data to support the research process.
         \par		The proposed use of computational statistics is likely to lead to new insights and has been defined in a way that make it easy to replicate.        
        \par		A walkthrough of the data analysis code is present and is justified very well. 
%
    \criterion{Artefact Test Plan}{---}
        \grade\fail 	There is no plan to validate, verify, and test the computing artefact, or it is inadequete.
        \grade 		There is an adequete plan to validate, verify, and test the computing artefact.
        \grade 		There is a competent plan to validate, verify, and test the computing artefact.
        \grade 		There is a very good plan to validate, verify, and test the computing artefact.
        \grade 		There is a excellent plan to validate, verify, and test the computing artefact.
        \grade 		There is a outstanding plan to validate, verify, and test the computing artefact.    
    %
\end{markingrubric}

%\section*{Additional Resources}

%\begin{itemize}
%    \item \url{http://www.opengl-tutorial.org}
%    \item \url{http://gamedev.stackexchange.com/questions/32876/good-resources-for-learning-modern-opengl-3-0-or-later}
%    \item \url{https://google.github.io/styleguide/cppguide.html}
%\end{itemize}
