\documentclass{../../../fal_assignment}
\graphicspath{ {../../../} }

\usepackage{enumitem}
\setlist{nosep} % Make enumerate / itemize lists more closely spaced
\usepackage[T1]{fontenc} % http://tex.stackexchange.com/a/17858
\usepackage{url}
\usepackage{todonotes}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\title{Worksheet 4: Interfaces and Interactions}
\author{Alcwyn Parker	}
\module{COMP280}
\version{1.0}

\begin{document}

\maketitle

\section*{Introduction}

\begin{marginquote}
``Design is really an act of communication, which means having a deep understanding of the person with whom the designer is communicating.''
\par --- \'Donald A. Norman
\end{marginquote}
%\marginpicture{flavour_pic}{
 %   \emph{SpaceChem} is a puzzle game in which players must apply computational thinking to build circuits which assemble
 %   chemical molecules.
%}

To complete this worksheet, you are expected to rapid prototype a simple user Interface in Unreal Engine or Unity. Once complete, the interface will be subject to a heuristic evaluation and then improved upon to accommodate the findings of the evaluation. 

To complete this worksheet: 

\begin{enumerate}[label=(\roman*)]
    \item \textbf{Design} a HUD for an FPS using Adobe XD or similar. The HUD interface must contain:
    \begin{itemize}
    	\item Enemy radar 
	\item Health bar
	\item Ammo
	\item Pause menu
	\item STRETCH GOAL - Controls window
    \end{itemize}
    \item \textbf{implement} the HUD in Unreal Engine or Unity
    \item \textbf{carry out} a heuristic evaluation on the HUD 
    \item \textbf{enhance} the initial HUD using the findings from the heuristic evaluation
    \item \textbf{STRETCH GOAL: } if you finish this worksheet early, ask a peer to evaluate your interface and use the new results to inform a second iteration of your interface. 
\end{enumerate}

\subsection*{Assignment Setup} 

Begin by \textbf{forking} the following Git repository: 

\hyperlink{https://github.com/Falmouth-Games-Academy/comp280-worksheet-4}{https://github.com/Falmouth-Games-Academy/comp280-worksheet-4} 

Use this repo to track all files related to this worksheet. Once you have completed the worksheet, make a pull request to receive formative feedback. 

To fulfil the requirements of this worksheet you are expected to submit evidence of:

\begin{itemize}
	\item an initial interface design in the form of interactive prototype;
	\item screenshots of the first implementation in engine;
	\item the results from a heuristic evaluation;
	\item and then screenshots of the final interface with enhancements based on the results from the heuristic evaluation
\end{itemize}


\section*{FAQ}

\begin{itemize}
	\item 	\textbf{What is the deadline for this assignment?} \\ 
			Each worksheet has its own formative deadline, specified on that worksheet and also communicated in class.
    		Falmouth University policy states that summative deadlines must only be specified on the MyFalmouth system.
    		
	\item 	\textbf{What should I do to seek help?} \\ 
    		You can email your tutor for informal clarifications. For informal feedback, make a pull request on GitHub. 
    		
	\item 	\textbf{How will I receive feedback on my work?} \\ 
    		You will be given verbal feedback on your work during the session in which it is marked.
    		If you require more in-depth feedback or discussion, please book an appointment with your tutor.
    		
    	\item 	\textbf{Is this a mistake?} \\ 	
    		If you have discovered an issue with the brief itself, the source files are available at: \\
    		\url{https://github.com/Falmouth-Games-Academy/bsc-assignment-briefs}.\\
    		 Please make a pull request and comment accordingly.
\end{itemize}

\rubrichead{Each individual worksheet is marked according to this rubric.}
\rubricfoot{Each worksheet is worth 11.1\% of the total marks for this assignment.}

\begin{markingrubric}
	\firstcriterion{Design of user interface}{30\%}
		\grade\fail	There is no functioning user interface
		\grade{There is a basic user interface with limited functionality}
		\grade{There is a basic user interface with some functionality}
		\grade{There is a user interface with good functionality}
		\grade{There is a well design user interface with much functionality}
		\grade{There is a well design user interface with much functionality}

		
    \criterion{Rigour}{50\%}
    	\grade\fail	There is no evaluation
		\grade{There is a very basic evaluation with little or no rigour}
		\grade{There is a basic evaluation with little rigour}
		\grade{There is a basic user interface with limited functionality}
		\grade{There is a basic user interface with limited functionality}
		\grade{There is a basic user interface with limited functionality}

\criterion{Depth of insight}{20\%}
    	\grade\fail	None of the issues identified in the evaluation have been addressed
		\grade{Few of the issues identified in the evaluation have been addressed}
		\grade{Some of the issues identified in the evaluation have been addressed}
		\grade{Many of the issues identified in the evaluation have been addressed}
		\grade{All of the issues identified in the evaluation have been addressed }
		\grade{A second iteration of the evaluation process has been carried out}

\end{markingrubric}

% https://www.reddit.com/r/unrealengine/comments/a7w2vq/how_to_design_a_fps_hud/
% https://www.youtube.com/watch?v=5Gt444eN7Rg&list=PLSlkDq2rO1t5r1tj6gLWD_EesQ8IZtN_h

\end{document}